Learning Incoherent Subspaces: Classification via Incoherent Dictionary Learning.

### 2014-01-13 manuscript.tex
classification figures

%%%%%%%%%%%%%%%%%%%%%%PACKAGES%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,graphicx}
\usepackage[english]{babel}
\usepackage[applemac]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{epsfig}
\usepackage{amsfonts,amssymb,amsmath,amsthm,bm}
\usepackage[boxruled,linesnumbered]{algorithm2e}
\usepackage{subfig,graphicx}
\usepackage{setspace}
\usepackage{enumitem}

@@

Figure
\begin{figure}
\includegraphics[width=\textwidth]{./Code/toyvisu.pdf}
\caption{\label{fig:toy}Synthetic data generated along one-dimensional subspaces of $\real^{2}$.}
\end{figure}
\subsubsection{Iris dataset}
\begin{figure}
\includegraphics[width=\textwidth]{./Code/fishervisu.pdf}
\caption{\label{fig:toy}Synthetic data generated along one-dimensional subspaces of $\real^{2}$.}
\end{figure}

@@

To assess the classification performance of the various techniques, we created a random $5$-fold partition of the training set used for cross-validation, and classified the transformed features using \Acronym{knn} with $5$ neighbours. The misclassification rate $\Acronym{mcr}$ defined as the number of misclassified samples divided by the total number of samples is displayed for the various methods in the first row of Table \ref{tab:fisher}. \Acronym{s-ipr} and \Acronym{lda} are both able to attain a $7\%$ misclassification error, improving on the $10\%$ obtained on the original features. The worst result is achieved by \Acronym{pca}, whose dimensionality reduction has the effect of mixing together features belonging to different classes, and achieves an error of $44\%$.
\begin{figure*}[!tb]
\begin{center}
%\includegraphics[width=\textwidth]{fisher3d.pdf}
\caption{\label{fig:fisher}Features transform for the fisheriris dataset. Red circular markers correspond to setosa, green square markers to versicolor and blue diamond markers to virginica.}
\end{center}
\end{figure*}
\begin{table}[!htb]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
  & none & \Acronym{pca} & \Acronym{lda} & \Acronym{s-ipr} \\
  \hline
  \textbf{\Acronym{mcr} - \Acronym{fisheriris}} & 0.10 & 0.44 & 0.07 & 0.07\\
\textbf{\Acronym{mcr} - \Acronym{usps}} & 0.343 & 0.433 & 0.359 & 0.315 \\
\hline
\end{tabular}
\caption{\label{tab:fisher} Misclassification error evaluated using different feature transform methods on the \Acronym{fisheriris} and \Acronym{usps} datasets (none indicates no feature transform).}
\end{center}
\end{table}
\subsection{Classification of the \Acronym{usps} digits dataset}
In order to evaluate the proposed method on a more challenging dataset that  contains signals of higher dimension, we run a similar experiment on the \Acronym{usps} digits dataset, which consists of a collection of $16\times 16$ pixels images of hand-written digits \footnote{http://www.cs.nyu.edu/~roweis/data.html.}. We selected the digits \Acronym{1}, \Acronym{3} and \Acronym{8} resulting in a total of $1405$ examples stored in the matrix $\Feas\in\ambient^{256\times 1405}$.

@@

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{bibliography.bib}

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%PACKAGES%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,graphicx}
\usepackage[english]{babel}
\usepackage[applemac]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{epsfig}
\usepackage{amsfonts,amssymb,amsmath,amsthm,bm}
\usepackage[boxruled,linesnumbered]{algorithm2e}
\usepackage{subfigure,graphicx}
\usepackage{setspace}
\usepackage{enumitem}

@@

Figure
\begin{figure}
\includegraphics[width=\textwidth]{./Code/toyvisu.pdf}
\caption{\label{fig:toyNewFea}Feature transform applied to the synthetic data in Figure \ref{fig:toy}. Different colours correspond to different classes, `+' and `o' markers represent samples taken from the training and test set respectively.}
\end{figure}
\subsubsection{Iris dataset}
\begin{figure}
\includegraphics[width=\textwidth]{./Code/Datasets/GetFisherIrisDataset.pdf}
\caption{\label{fig:fisher3} First three features of the `iris' dataset depicting measurements of sepal length, sepal with and petal length of three iris species.}
\end{figure}
\begin{figure}
\includegraphics[width=\textwidth]{./Code/fishervisu.pdf}
\caption{\label{fig:toyNewFea}Feature transform applied to the iris data in Figure \ref{fig:fisher3}. Different colours correspond to different classes, `+' and `o' markers represent samples taken from the training and test set respectively.}
\end{figure}

\subsection{Classification results}
\begin{figure}
\centering
\subfigure{\includegraphics[width=.45\textwidth]{Code/Util/fisheriris.pdf}}
\subfigure{\includegraphics[width=.45\textwidth]{Code/Util/balance.pdf}}
\subfigure{\includegraphics[width=.45\textwidth]{Code/Util/parkinsons.pdf}}
\subfigure{\includegraphics[width=.45\textwidth]{Code/Util/sonar.pdf}}
\caption{}
\end{figure}

@@

To assess the classification performance of the various techniques, we created a random $5$-fold partition of the training set used for cross-validation, and classified the transformed features using \Acronym{knn} with $5$ neighbours. The misclassification rate $\Acronym{mcr}$ defined as the number of misclassified samples divided by the total number of samples is displayed for the various methods in the first row of Table \ref{tab:fisher}. \Acronym{s-ipr} and \Acronym{lda} are both able to attain a $7\%$ misclassification error, improving on the $10\%$ obtained on the original features. The worst result is achieved by \Acronym{pca}, whose dimensionality reduction has the effect of mixing together features belonging to different classes, and achieves an error of $44\%$.

\begin{table}[!htb]
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
  & none & \Acronym{pca} & \Acronym{lda} & \Acronym{s-ipr} \\
  \hline
  \textbf{\Acronym{mcr} - \Acronym{fisheriris}} & 0.10 & 0.44 & 0.07 & 0.07\\
\textbf{\Acronym{mcr} - \Acronym{usps}} & 0.343 & 0.433 & 0.359 & 0.315 \\
\hline
\end{tabular}
\caption{\label{tab:fisher} Misclassification error evaluated using different feature transform methods on the \Acronym{fisheriris} and \Acronym{usps} datasets (none indicates no feature transform).}
\end{center}
\end{table}
\subsection{Classification of the \Acronym{usps} digits dataset}
In order to evaluate the proposed method on a more challenging dataset that  contains signals of higher dimension, we run a similar experiment on the \Acronym{usps} digits dataset, which consists of a collection of $16\times 16$ pixels images of hand-written digits \footnote{http://www.cs.nyu.edu/~roweis/data.html.}. We selected the digits \Acronym{1}, \Acronym{3} and \Acronym{8} resulting in a total of $1405$ examples stored in the matrix $\Feas\in\ambient^{256\times 1405}$.

@@

\bibliographystyle{IEEEbib}
\bibliography{bibliography.bib}
\end{document}
